---
title: "Relationship Between Energy Costs and the Amount of Rooms, Electronics, and Appliances a Multifamily Household Uses in 2023"
author: "Kei Matsumoto"
thanks: "Project repository available at: [https://github.com/keimatsumoto1/261aFinalProject](https://github.com/keimatsumoto1/261aFinalProject)"
date: 12/1/2025
date-format: long
abstract: "Energy bills are a significant factor when owning or buying a house. Appliances such as dishwashers, washing machines, and refrigerators are one of many items people use almost every day that consume energy. Aside from appliances, devices like televisions, computers, and even lightbulbs in multiple rooms will also contribute to the overall bill. With this in mind, how does the amount of rooms and appliances affect the energy cost per square feet/year for multifamily houses? A dataset by Fannie Mae was constructed from a survey that records the overall energy/water consumption of multifamily households during 2023 with characteristics of each building being the parameters. In this paper, we will be fitting a multiple linear regression to see if there is a relation between the number of room/units, bathrooms, elevators, appliances, and computers with energy fees measured in dollars per square feet per year. Overall, we were not able to conclude that there is a correlation between any of the parameters with energy cost due to an overabundance of missing values and assumption violations."
format: pdf
number-sections: true
editor: 
  markdown: 
    wrap: 72
---

```{r}
#| include: false
#| warning: false
#| message: false
# load libraries
library(readr)
library(dplyr)
library(ggplot2)
library(olsrr)
library(readxl)
library(stargazer)
library(Metrics)

set.seed(111)
X2023_Multifamily_Survey_dataset_FINAL <- read_excel("2023_Multifamily_Survey_dataset_FINAL.xlsx", 
                                                     sheet = "Database", skip = 1)

data <- X2023_Multifamily_Survey_dataset_FINAL

data2 <- subset(data, select = c( `Grand Total Number of Bedrooms`, `Grand Total Number of Units`, `Number of Kitchens`, `Number of In-Unit Washer/Dryer Units`, `Number of Dishwashers`, `Number of Elevators`, `Number of Resident Bathrooms`, `Number of Computers in Common Areas`, `Energy Cost ($/sqft/yr)`))

data_with_state <- subset(data, select = c( State, `Grand Total Number of Bedrooms`, `Grand Total Number of Units`, `Number of Kitchens`, `Number of In-Unit Washer/Dryer Units`, `Number of Dishwashers`, `Number of Elevators`, `Number of Resident Bathrooms`, `Number of Computers in Common Areas`, `Energy Cost ($/sqft/yr)`))

State_total <- data_with_state %>%
  count(State) %>% arrange(desc(n))

#check total amounts of state data
print(State_total)


data2 <- as.data.frame(lapply(data2, as.numeric))

data2 <- data2 %>%
  rename(Bedrooms = Grand.Total.Number.of.Bedrooms, Units = Grand.Total.Number.of.Units, Kitchens = Number.of.Kitchens, WasherDryer = Number.of.In.Unit.Washer.Dryer.Units, Dishwashers = Number.of.Dishwashers, Elevators = Number.of.Elevators, Bathrooms = Number.of.Resident.Bathrooms, Computers = Number.of.Computers.in.Common.Areas, EnergyCost = Energy.Cost....sqft.yr. )


train <- floor(0.7 * nrow(data2))
trains <- sample(seq_len(nrow(data2)), size = train)
data_train <- data2[trains, ]
data_test <- data2[-trains, ]

#check amount of na's per column
na_total <- sapply(data_train, function(x) sum(is.na(x)))
print(na_total)

```

# Introduction

When people are looking at renting an apartment or buying a house, many
factors will have to be considered. For example, living space, location,
number of rooms, and number of bathrooms are a couple of standard
factors that people will look into. In addition to these factors, energy
and water consumption are also some components that people may consider
due to the energy and water bills being key payments which add on to
rent. So can we predict ahead of time what our energy cost will be by
the amount of rooms and appliances a household will have? According to
the International Energy Agency, there have been long-running policies
for appliances and electrical devices that are “now typically consuming
30% less energy than they would have done otherwise.” (IEA, 2021) These
policies have been operating the longest in the United States and the
European Union which helps appliances reduce their costs, energy
consumption, and CO2 emissions. However, even though these appliances
have been reducing the amount of energy consumed over the years,
electricity bills are still significantly costly. Saveonenergy conducted
a survey in 2022 and found that 62% of the results saw an increase in
their electricity bills. (Saveonenergy, 2025) Many outside factors such
as people over-using devices when not needed, using old appliances, and
using more than necessary electronic devices are considerable when
looking back on how people used electricity. The over-abundance of
electronic devices in this current generation may contribute to a larger
usage of energy even if each device has been improving their efficiency.

By being able to see if energy costs have a relation to the number of
rooms and/or electronics, we can possibly be able to predict what our
future energy cost will be with the house that we plan to buy/rent. It
will allow new homeowners to budget how much money they will have to
save for energy bills within a year. In addition, it will allow property
owners of complexes like apartments to find out how much the rent will
need to be through the amount of electronics the building will require.

This paper will be strictly covering multiple linear regression models
as well as variable selection with no further methods. This will allow
us to see if there is a correlation between energy costs and the number
of room types and/or electronics to see if we can predict future
multifamily building energy costs. We will conclude that there will not
be a significant model that can be produced through either method due to
assumption violations of normality, equal variance, and linearity.
Within multiple linear regression, there is no possible way to find our
prediction with our full model and through variable selection minimizing
Mallow's cp and maximizing the adjusted r-squared. The full model's
residual plot hints that there could possibly be a better model such as
a polynomial regression due to the parabola-like trend being visible,
with external issues of an overabundance of missing points being
prominent. The multiple linear regression and variable selection will be
analyzed through the programming language R and packages such as
“ggplot2”, “dplyr”, "Metrics", and “olsrr” to conduct and visualize our
regression models. (R Core Team, 2023)

This paper will include the description of the data set, the description
of the methods used, the core assumptions our analysis will require for
a valid prediction and inference, and the explanation of our results.

# Data {#sec-data}

The data we are looking into for this paper is provided by Fannie Mae
which is the primary provider of data to companies such as Energy Star
to analyze a building’s energy efficiency. In contrast to commercial
buildings, energy and building data is not federally supported and does
not have an open data set to the public. To provide information to
engineers, Fannie Mae started collecting multifamily building data in
2012 to further find possible ways to decrease the energy and water
consumption of multifamily buildings. (Fannie Mae, 2023) The data set by
Fannie Mae consists of a survey conducted in 2023 from March 1st to
August 31st where Fannie Mae reaches out to many mortgage companies to
ask for specific information for multifamily buildings similar to the
national survey of utility consumption. In addition, Fannie Mae will
reach out to properties and send property data collectors (PDC) to
physically note down the key attributes of the properties. These PDCs
must have extensive training and follow the "Property Data Collector
Independence Requirements" to not have any bias during the data
collection. (Fannie Mae, 2023)

The energy cost of a building is calculated by the total cost of energy
spent within one year divided by the total area of the building in
square feet. The energy spent is divided by the total area to be able to
compare buildings on an equal scale. Larger buildings will need to spend
more energy on appliances such as HVAC and lighting which will change
the scaling of our model drastically if not divided by square feet.
Energy spent includes multiple various energy sources such as
electricity, oil, and gas. Unfortunately this data set does not control
the appliances' and electronics' age as we do not know if the household
is up to date with upgraded technology. As stated before in the
introduction, newer appliances have been decreasing their energy usage
but we are unable to control this for this paper.

Some factors to consider within this data is that there are many missing
values within each parameter which can affect the overall skewness and
quality of our analysis. The columns that consisted of the most missing
values were computers and bathrooms which can be considered for removal.

In addition, this data is collected from buildings nationwide which can
lead to larger variances and skewed results if certain states have more
data than others. For energy consumption, location can affect the
overall usages of heaters and coolers and different appliances. Within
our data set, we found that most of the observations consists of
California being 494 out of 2273 entries and then Massachusetts being
180 entries. This highlights that there is a large variance between the
amount of data each state has in our study which can lead to our energy
costs being skewed which will be further discussed within the Discussion
section.

The data consists of the following parameters after being cleaned in R.
The data was cleaned to strictly show the parameters of interest which
directly include the usage of energy sources within the building:

-   Bedrooms: The total number of bedrooms in the building.

-   Units: The total amount of units in the building.

-   Kitchens: The number of kitchens within the building.

-   Dishwashers: The number of dishwashers within the building.

-   WasherDryer: The number of washers and dryers within the building.
    Elevators: The number of elevators within the building.

-   Bathrooms: The number of bathrooms within the building.

-   Computers: The number of computers within the building.

-   EnergyCost: The total cost for the energy usage of the building.
    Calculated by the total cost divided by the total square feet in one
    year. (\$/sqft/yr)

# Methods {#sec-methods}

In this paper, we will be conducting a multiple linear regression to
analyze the relationship between the number of rooms, units, elevators,
bathrooms, appliances, and computers, with the energy cost of
multifamily buildings in 2023.

$$Y_i = \beta_0 +\beta_1 X_{1,i} + \beta_2 X_{2,i} +\beta_3 X_{3,i} +\beta_4 X_{4,i} +\beta_5 X_{5,i} + \beta_6 X_{6,i} +\beta_7 X_{7,i} +\beta_8 X_{8,i} + \varepsilon_i$$

-   $\beta_0$ will represent the intercept of the model which will be
    the expected energy cost when all parameters are 0.

-   $\beta_1$ will represent the coefficient for Bedrooms which will be
    the expected change in energy cost when the number of bedrooms
    increases by 1 and all other parameters are held constant.

-   $\beta_2$ will represent the coefficient for Units which will be the
    expected change in energy cost when the number of building units
    increases by 1 and all other parameters are held constant.

-   $\beta_3$ will represent the coefficient for Kitchens which will be
    the expected change in energy cost when the number of kitchens
    increases by 1 and all other parameters are held constant.

-   $\beta_4$ will represent the coefficient for WasherDryer which will
    be the expected change in energy cost when the number of washers and
    dryers increases by 1 and all other parameters are held constant.

-   $\beta_5$ will represent the coefficient for Dishwashers which will
    be the expected change in energy cost when the number of dishwashers
    increases by 1 and all other parameters are held constant.

-   $\beta_6$ will represent the coefficient for Elevators which will be
    the expected change in energy cost when the number of elevators
    increases by 1 and all other parameters are held constant.

-   $\beta_7$ will represent the coefficient for Bathrooms which will be
    the expected change in energy cost when the number of bathrooms
    increases by 1 and all other parameters are held constant.

-   $\beta_8$ will represent the coefficient for Computers which will be
    the expected change in energy cost when the number of computers
    increases by 1 and all other parameters are held constant.

-   $Y_i$ will represent the true energy cost of the i-th multifamily
    household.

-   $X_{j,i}$ will represent the given constants of each parameter for
    the i-th multifamily household where j is 1 - 8.

-   $\epsilon_i$ will represent the random error with a mean of zero and
    finite variance of $\sigma^2$.

We will also be conducting variable selection with the usage of olsrr’s
“step_all_possible” function which will calculate a Mallow's CP. We will
then choose the combination of parameters that consists of the smallest
Mallow’s CP and highest adjusted R-squared for prediction which is the
following equation. A low Mallow's cp will allow us to have the lowest
bias with the best possible fit with our adjusted R-squared.

$$C_p = \frac{SSE_p}{\hat{s^2}} + 2p - n$$$SSE_p$ represents the sum of
squared errors with p parameters. $s^2$ represents the full model's mean
squared error with n representing the number of observations.

Some drawbacks for variable selection that we must consider are that our
coefficients will be biased and overestimated which will invalidate our
inferences for variables such as R\^2 and confidence interval analysis.
We will be conducting variable selection solely as an exploratory
comparison with the full model to see if we can determine a model with
valid assumptions to predict energy costs. Both model analysis will be
conducted through the programming language R utilizing multiple packages
such as ggplot2, dplyr, oslrr, Metrics, and readr. (R Core Team, 2023)

# Assumptions

The assumptions we need to validate for our analysis are the following:

1\. Validity where the variables are appropriate for the question we are
studying.

2\. Representativeness where the sample data represents the population
of interest.

3\. Linearity where following function must be true: $E(Y_i | X_i)$ =
$\beta_0 +\beta_1 X_{1,i} + \beta_2 X_{2,i}... + \beta_2 X_{8,i}$.
Independence of errors where all errors of our model are assumed to be
independent.

5\. Equal variance of errors where our errors’ variances must be equal
throughout the model.

6\. Normality of errors where our errors must be normally distributed.

7\. Multicollinearity where our variables must not have a correlation
with each other.

# Results - Full Model

```{r lm}
#| echo: false
#| warning: false
#| message: false
#| 

lm1 <- lm(EnergyCost~., data = data_train)


```

-   $\hat{\beta_1}$ = 0.002945, p = 0.3327

-   $\hat{\beta_2}$ = 0.0045643, p = 0.5730

-   $\hat{\beta_3}$ = -0.0007534, p = 0.9225

-   $\hat{\beta_4}$ = 0.0011886, p = 0.4019

-   $\hat{\beta_5}$ = -0.0055313, p = 0.236

-   $\hat{\beta_6}$ = 0.3145418, p = 0.0102

-   $\hat{\beta_7}$ = -0.0029454, p = 0.2965

-   $\hat{\beta_8}$ = -0.0292474, p = 0.2777

Within our multiple linear regression, we found that the number of
elevators($\hat{\beta_6}$) had the lowest p-value being all less than
0.05. This highlights that for our full model, the only coefficient that
we can conclude that are possibly non-zero is the number of elevators.
The other coefficients may truly have a relation to the energy cost of a
multifamily, but we are unable to determine this with just multiple
linear regression. We will not be considering the intercept of our data
as a building with no rooms will not provide support for the research
topic.

This means that:

-   When all other parameters are held constant, an increase of one
    elevator will increase the yearly energy cost of the building by
    0.3145418 dollars per sqft on average.

Aside from the p-values we found that dishwashers, kitchens, bathrooms,
and computers have a negative slope. These results imply that on
average, an increase of each of those electronics or rooms by one with
all other parameters held constant would decrease the energy cost. Each
of these coefficients respectfully have p-values higher than 0.1 besides
bathrooms which can provide support that the number of dishwashers,
kitchens, bathrooms and computers may not have any influence to energy
cost even if the slope parameters are found to be negative. Overall,
without considering p-values, we can notice that all of our parameters
besides the amount of elevators will not change the overall energy price
by a large amount. The amount of elevators have considerably a large
change to the energy cost of the overall buildings on average which
could lead to elevators being a large consumer of energy.

We found that our adjusted R-squared value resulted to be 0.2096
indicating that our model explains only 20.96% of the total variance of
our data highlighting that our model may not be suited to provide a good
fit for the data.

To check our assumptions we will look into the residual plot between
fitted values and the residual values of our full model.

```{r residual}
#| echo: false
#| fig-pos: "H"
#| warning: false
#| message: false
#| fig-cap: "Residual plot of the x axis being the fitted values and the y axis being the residuals for the full model with Enery Cost as the response."
p <- data.frame(
  res = resid(lm1),
  fit = fitted(lm1)
)
ggplot(p, aes(x = fit, y = res)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ylab("Residual (observed - fitted)") +
  xlab("Fitted value") +
  ggtitle("Residuals vs. Fitted plot")


```

As we can see, the residual plot is not random and we can notice a
parabola-shaped trend with a slight right skew. Due to this, the
assumptions for linearity and equal variance will be violated suggesting
that multiple linear regression is not suitable for this data. The
parabola-shaped trend can possibly indicate that a polynomial
relationship or other transformations might be suited for this data set.
The violation of equal variance may likely cause incorrect inferences
within our coefficients leading to coefficients that we may consider
correlated being truly uncorrelated. The strength of our accuracies may
not be trusted with unequal variances for our model.

Next we will check for the normality assumption by analyzing the QQ-plot
of our multiple linear regression.

```{r qq}
#| echo: false
#| fig-pos: "H"
#| warning: false
#| message: false
#| fig-cap: "The QQ plot between the sample (x) and theoretical (y) quantiles with the line representing the theoretical normal distribution"

residual = residuals(lm1)
df1 = data.frame(residuals = residual)
qqnorm(residual, main = "Normal Q-Q Plot for The Full Model")
qqline(residual)

```

By analyzing the QQ plot of our model, we can see a deviance from the
normal distribution on the head of the plot. This violates the
assumption that our errors are normally distributed. With errors that
are not normally distributed, our p-values for our coefficients may be
incorrect leading to incorrect conclusions. We can see that our head of
the QQ plot being far from the normal line connects to our previous
finding with the residual plot being right skewed and having
heteroscedasticity.

An extreme issue within this study is that our data includes too many NA
values. The multiple linear regression removed 1556 out of 1591
observations from our data only using 35 total observations. The
uncertainty from our data is likely due to the sample size being
significantly low violating multiple assumptions such as normality and
error independence. Due to the amount of observations being 35, the
assumption of normality is critical and influences our p-values for our
coefficients making them unreliable.

Due to our linearity, equal variance, and error normality assumptions
being violated and our number of observations being low, multiple linear
regression for the full model may not be a suitable model to conduct
predictions to see if the number of rooms, electronics, and appliances
have an influence on a multifamily building's energy cost.

# Results - Variable Selection

```{r var selection}
#| echo: false
#| warning: false
#| message: false

lm_ols <- ols_step_all_possible(lm1)
lmsorted <- lm_ols$result
lmsorted <- lmsorted[order(lmsorted$cp),]

lm3 <- lm(EnergyCost~ Units + WasherDryer + Elevators + Bathrooms, data = data_train)

```

When conducting variable selection using the olsrr method
"ols_step_all_possible," we found that the combination of our parameters
with the lowest Mallow's cp was the number of units, number of
washers/dryers, the number of elevators within a multifamily building. A
low Mallow's cp will provide a model that includes the lowest bias

We will then look into a multiple linear regression model of:
$$Y_i = \beta_0 +\beta_1 X_{1,i} + \beta_2 X_{2,i} + \beta_3 X_{3,i} + \beta_4 X_{4,i} + \varepsilon_i$$

Where:

-   $\beta_1 X_{1,i}$ will represent the coefficient for Units which
    will be the expected change in energy cost when the number of units
    increases by 1 and all other parameters are held constant.

-   $\beta_2 X_{2,i}$ will represent the coefficient for WasherDryer
    which will be the expected change in energy cost when the number of
    washers/dryers increases by 1 and all other parameters are held
    constant.

-   $\beta_3 X_{3,i}$ will represent the coefficient for Elevators which
    will be the expected change in energy cost when the number of
    elevators increases by 1 and all other parameters are held constant.

-   $\beta_4 X_{4,i}$ will represent the coefficient for Bathrooms which
    will be the expected change in energy cost when the number of
    bathrooms increases by 1 and all other parameters are held constant.

The multiple linear regression using this model resulted with
$\hat{\beta_0}$ = 0.9487642, $\hat{\beta_1}$ being 0.0003508 with a
p-value of 0.8146, $\hat{\beta_2}$ being 0.0006115 with a p-value of
0.3009, $\hat{\beta_3}$ being 0.0593361 with a p-value of 0.0492, and
$\hat{\beta_4}$ being -0.0005799 with a p-value of 0.5173.

This means that:

-   When all parameters are 0, the estimate energy cost on average will
    be 0.9487642 dollars per sqft.

-   When all other parameters are held constant, an increase of one unit
    will increase the yearly energy cost of the building by 0.0003508
    dollars per sqft on average.

-   When all other parameters are held constant, an increase of one
    washer/dryer unit will increase the yearly energy cost of the
    building by 0.0006115 dollars per sqft on average.

-   When all other parameters are held constant, an increase of one
    elevator will increase the yearly energy cost of the building by
    0.0593361dollars per sqft on average.

-   When all other parameters are held constant, an increase of one
    bathroom will decrease the yearly energy cost of the building by
    0.0005799 dollars per sqft on average.

Our p-values for units washer/dryers and bathrooms are quite high being
larger than 0.1 leading to a possible lack of a correlation with energy
cost. On the other hand, the number of elevators include a slightly low
p-value being less than 0.05 highlighting possible relations to energy
costs. However, with the issues with large bias from using variable
selection can lead to misinterpretations with these coefficient p-values
so we are still unable to say if our four selected parameters are truly
related with the energy cost.

```{r residual2}
#| echo: false
#| fig-pos: "H"
#| warning: false
#| message: false
#| fig-cap: "Residual plot of the x axis being the fitted values and the y axis being the residuals for the variable selected model with Enery Cost as the response."
p <- data.frame(
  res = resid(lm3),
  fit = fitted(lm3)
)
ggplot(p, aes(x = fit, y = res)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ylab("Residual (observed - fitted)") +
  xlab("Fitted value") +
  ggtitle("Residuals vs. Fitted plot")


```

By observing our residual plot of the model using variable selection, we
can notice that there are no significant trends to violated linearity
where all the points are randomly scattered. However, the distribution
of the points are still skewed to the right and are forming a funnel
shape violating the equal variance of errors assumption. This highlights
that even when using variable selection to find the best possible
combination of parameters, the usage of multiple linear regression may
not be suited for this data. Having an unequal variance within our
regression can cause misinterpretations of our coefficients. We may be
concluding that our coefficients may be insignificant when they may
truly be significant and have a correlation with energy costs.

```{r qq2}
#| echo: false
#| fig-pos: "H"
#| warning: false
#| message: false
#| fig-cap: "The QQ plot between the sample (x) and theoretical (y) quantiles with the line representing the theoretical normal distribution for the Varaible selection regression model"

residual = residuals(lm3)
df1 = data.frame(residuals = residual)
qqnorm(residual)
qqline(residual)

```

The QQ plot for the variable selected model is also similar scenario
with the original full model where the tail and head of the data are
both spread apart from the normal distribution line implying that the
errors are not normal for this model as well. In contrast to the full
model, there includes a larger amount of observations within the tail
that is far from the normal line with most other observations staying
fairly normal. By combining the two assumption violations, our data may
not be suitable for predictions for energy cost with any combination of
multiple linear regression. This suggests that other methods such as
non-linear regression models may be preferred when predicting a
multifamily building's energy cost from the amount of rooms,
electronics, and appliances it includes.

# Results - Predictions

```{r pred}
#| echo: false
#| fig-pos: "H"
#| warning: false
#| message: false


na_Test <- na.omit(data_test)
predFull <- predict(lm1, newdata = na_Test)
predVS <- predict(lm3, newdata = na_Test)

rmseFull <- rmse(na_Test$EnergyCost, predFull)
rmseVS <- rmse(na_Test$EnergyCost, predVS)

na_Train <- na.omit(data_train)
predFull2 <- predict(lm1, newdata = na_Train)
predVS2 <- predict(lm3, newdata = na_Train)

rmseFull2 <- rmse(na_Train$EnergyCost, predFull)
rmseVS2 <- rmse(na_Train$EnergyCost, predVS)

```

When calculating predictions, we found that our RMSE for our full and
our variable selection models ended up being 0.662981 and 0.7088105
respectively. Although these numbers may seem small at glance, the range
of energy cost within our test set will vary from 0.1 to 3 making 0.66
and 0.7 being large errors within our scale. When comparing the overall
accuracy between the full and variable selected model, we can see that
our full model predicts the energy costs slightly more accurate than our
variable selected mode. However, due to both RMSE values being high,
neither model will be preferred for predicting the overall future energy
costs.

An extreme issue that we found within both the test and training set is
the issue with missing values. Our predictions can only look into 16 out
of 682 of our observations for our test set and 31 out of 1591
observations in our training set. When looking into the training set's
predictive power, we do see similar results with both RMSEs being
.9673084 and .830092 with poor accuracies overall. Further, the
scaffolding issues with our assumption violations, missing values, and
poor predictive accuracies will not allow us to see if there is a true
relationship between energy costs and room, units, electronic, and
appliance numbers.

# Discussion {#sec-discussion}

When observing the overall data set after conducting variable selection,
a major issue within the data set is that each observation includes
missing values in at least one column leading to many observations being
disregarded within our regressions. A possible solution to this issue
would be to remove specific variables from our multiple linear
regression. However, due to many combinations of parameters also having
similar issues with missing values, the removal of columns would lead to
individual simple linear regressions. Although we can use simple linear
regression, our conclusions can include a large bias leading to invalid
connections between the predictor and the response variables directing
us into incorrect results because we are not considering different
parameters at the same time. 

Another limitation that we have within our data is the variance in
locations. The data set consists of observations primarily from
California and different amounts of observations in other States.
Location can be a large factor when considering our conclusions as a
possible reason why our parameters do not correlate to energy cost could
be due to different locations using different amounts of appliances.
Weather conditions and temperature variances between States is one of
many factors that can cause energy consumption variances. A study in
2023 from the U.S. The Energy Information Administration discovered that
in 2020, “air conditioning accounted for 28% of total site energy usage
in Florida but just 2% in Maine.” (EIA, 2023) Due to different states
consuming energy with different intensities, it would be difficult to
conclude that one specific appliance or electronic device can lead to
higher energy costs. 

In addition, outside variables that are not in our data set such as car
culture can affect the costs of energy. California had the most
observations within our data set and according to The U.S. Department of
Energy, California consisted of 35% of electric vehicle registrations
within the United States in 2023. (U.S. Department of Energy, 2023)
Owning an electric vehicle can increase the usage of electricity within
a household from overnight and daily charging. Outside variables that
are not able to be calculated within this data set can also affect why
our regression concluded with a lack of correlations within our full
model and any combination of variables. 

Due to many outside factors, missing variables, and variance within
locations, we cannot conclude whether or not the number of rooms,
elevators, bathrooms, appliances, and electronics, have a relationship
with the overall energy cost of a multifamily building. There can be
many other methods to test to see if the amount of rooms, electronics,
and appliances truly do relate to energy costs. Possible methods include
tightening the study into separate States or locations to see if
electronics in specific states have a relation to energy costs. This can
provide less possible missing observations as well as fix the variance
within locations. Another possible method can be to use a different
model such as a polynomial regression. We noticed a parabola-shaped
pattern within our residual plot for our full model highlighting how
there can be a possible better fit for a polynomial. This can fix the
heteroskedasticity we noticed in our multiple linear regression model
validating the assumption of equal variance in errors allowing us to
possibly conclude connections between the relationship of energy costs
and our parameters.

# References

*Appliance standards and labelling is highly effective at reducing
energy use, new joint study finds - News*. (n.d.). IEA.
https://www.iea.org/news/appliance-standards-and-labelling-is-highly-effective-at-reducing-energy-use-new-joint-study-finds

*Electricity Bills By State Monthly Report \| SaveOnEnergy®*. (n.d.).
Www.saveonenergy.com.
https://www.saveonenergy.com/resources/electricity-bills-by-state/

Hamner B, Frasco M (2018). *Metrics: Evaluation Metrics for Machine
Learning*. doi:10.32614/CRAN.package.Metrics
<https://doi.org/10.32614/CRAN.package.Metrics>, R package version
0.1.4, <https://CRAN.R-project.org/package=Metrics>.

Hebbali A (2024). *olsrr: Tools for Building OLS Regression Models*. R
package version 0.6.1.9000,
https://github.com/rsquaredacademy/olsrr, <https://olsrr.rsquaredacademy.com/>.

*How Much Electricity Do My Home Appliances Use?* (2019).
PublicWebsiteSitefinity.
https://www.igs.com/energy-resource-center/energy-101/how-much-electricity-do-my-home-appliances-use

H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag
New York, 2016.

R Core Team (2023). *R: A Language and Environment for Statistical
Computing*. R Foundation for Statistical Computing, Vienna, Austria.
<https://www.R-project.org/>.

“2023 Multifamily Energy & Water Survey \| Fannie Mae.” *Fanniemae.com*,
2023,
multifamily.fanniemae.com/financing-options/green-financing/2023-multifamily-energy-water-survey.
Accessed 10 Dec. 2025.

U.S. Department of Energy. (2022, June). *Alternative Fuels Data Center:
Maps and Data - Electric Vehicle Registrations by State*.
Afdc.energy.gov; U.S. Department of Energy.
https://afdc.energy.gov/data/10962

*U.S. Energy Information Administration - EIA - Independent Statistics
and Analysis*. (n.d.). Www.eia.gov.
https://www.eia.gov/pressroom/releases/press535.php

Wickham H, Hester J, Bryan J (2023). \_readr: Read Rectangular Text
Data\_. R package version 2.1.4,
https://CRAN.R-project.org/package=readr.
